\section{Introduction}
\label{sec.introduction}
This document describes the design and considerations of the \emph{LaPizzeria}
project. The goal of the project is to design, implement and document a web
shop, which enables users to browse a list of pizzas, add/remove pizzas to a
shopping chart and checkout. Please find out more about the requirements and specifications of the project
\href{http://www.itu.dk/people/brabrand/IWJX/LaPizzeria.pdf}{here}\footnote{\url{http://www.itu.dk/people/brabrand/IWJX/LaPizzeria.pdf/}}.
You can browse the source code of the project at:
\begin{itemize}
  \item
  JSP at
  \href{http://subversion.assembla.com/svn/ws_course/}{svn}\footnote{\url{http://subversion.assembla.com/svn/ws_course/}}.
  \item JSF at
  \href{https://bitbucket.org/KarolySzanto/web_development}{mercurial}\footnote{\url{https://bitbucket.org/KarolySzanto/web_development/}}.
\end{itemize}
The report is organized as follows: a short overview and motivation for the
project, the description of the system (requirements, design and
implementation (MVC pattern), usage of the system), discussion highligthinh the
main differences between the two implementations.

\subsection{Overview}
\label{sec.introduction.overview}
The purpose of the system is to implement an online web shop to provide cutomers
with the possiblity of placing orders on the internet. The web shop
should have 2 types of users: customers and administartors. Customers should
have the option of registering, browsing a list of items, add/remove items to/from a shopping chart
and place an order. An administrator should be able to manage the list of items
(add/remove) after logging in.
\subsection{Motivation}
\label{sec.introduction.motivation}
The web shop will be implemented using JSP (Java Server Pages) and JSF (Java
Server Faces) in order to get acquainted with the basic concepts. It will also provide a good basis for assesing the
advantages and disadvantages of using these technologies.
